---
title: "ClinReport R package"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%"
)
```

[![CRAN status](https://www.r-pkg.org/badges/version/ClinReport)](https://cran.r-project.org/package=ClinReport) 
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
![cranlogs](http://cranlogs.r-pkg.org./badges/officer)

## Introduction

Initially, the aim of ClinReport is to create statistical outputs (tables and graphics) in 'Microsoft Word'
according to 'clinical standards' of reporting. 

Since the formatted outputs are it's suitable for any publications, it can also be used outside the scope of clinical trials.

## Installation

You can install the released version of ClinReport from [CRAN](https://CRAN.R-project.org) with:

```r
install.packages("ClinReport")
```


## Basic example

```{r, include=T}

library(ClinReport)
library(officer)
library(flextable)

# Load data

data(data)

# Descriptive statistics (Numerical response and 2 explicative variables):

tab1=report.quanti(data=data,y="y_numeric",
		x1="GROUP",x2="TIMEPOINT",at.row="TIMEPOINT",subjid="SUBJID")
tab1

# You can have the corresponding graphic:

gg=plot(tab1,title="Mean response evolution as a function of time by treatment group",
 legend.label="Treatment groups",ylab="Y mean")
gg

```

# Put the results in a docx document  with officer  


```r

doc=read_docx()
doc=report.doc(tab1,title="Example of a quantitative descriptive table",doc=doc) 

# See the results

file=paste(tempfile(),".docx",sep="")
print(doc, target =file)

#shell.exec(file)

```


