---
title: "ClinReport Vignette 1: Clinical Standards for Reporting Statistics"
author: "Jean-Francois COLLIN"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ClinReport Vignette 1: Clinical Standards for Reporting Statistics}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Clinical Standards

There is no official guidance regarding the format of the statistical tables used for clinical trial reporting,
but there are implicit standards that are most frequently used.

Those standards are given below (in no specific order):

>
*	If statistics are reported by treatment group, display the statistics by treatment groups in columns
*	Do not display horizontal or vertical lines in the body of the table 
*	When there are statistics reported for several parameters or if they are reported by level of another factor
in the same table, split the results with empty rows
*	Add the number of subjects randomized in the column headers 
*	Each output should be numbered
*	Each output should have a title
*	The number of digits should be the same in all cells 
*	Always display the unit of the measured parameter in its label between parenthesis
*	Police Headers should be bolded
*	Usually for baseline characteristics add the Total column along with the treatment groups
*	Use (most of the time) the *Times New Roman* police


For quantitative statistics:

>
*	Report systematically the standard deviation between parenthesis after the mean: *mean(SD)*
*	Report the interval Q1 Q3 between brackets: *[Q1;Q3]*
*	Report the interval Min Max between brackets: *[Min;Max]*


For qualitative statistics:

>
*	Report the percentages and the number of observations *N(%)* or *%(N)*


For Least-Square Means statistics and P-values:

>
*	Report systematically the standard error between parenthesis after the estimate *estimate(SE)*
*	Report the 95% confidence interval between brackets: *[Lower Bound;Upper Bound]*
*	If P<0.001, display *P<0.001* instead of the value of P

#  Example with `ClinReport`

The purpose of the package **ClinReport** is to make Clincal Reporting easy according to those standards.

Those are the default reporting options in the package **ClinReport** so few lines of code are necessary
as can be seen in the example below:

```{r, echo = TRUE, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(reshape2)
library(nlme)
library(emmeans)
library(car)
```  


```{r, include=TRUE}
library(ClinReport)
library(officer)
library(flextable)

data(data)

# Default quantitative stat desc

tab1=report.quanti(data=data,y="y_numeric",
		x1="GROUP",y.label="Quantitative response (units)",
		subjid="SUBJID",total=T)
		
# Default qualitative stat desc

tab2=report.quali(data=data,y="y_logistic",
		x1="GROUP",y.label="Qualitative response",
		subjid="SUBJID",total=T)

# Binding them into a single table

tab=regroup(tab1,tab2)

# Create formatted output for Microsoft Word

doc=report.doc(tab,title="Table of classic descriptive statistics (qualitative and quantitative parameter)",
		colspan.value="Treatment group", init.numbering =T )			

doc
```


By default, this table respect all the standards described above.

















