---
title: "ClinReport Vignette 1: Clinical Standards for Reporting Statistics"
author: "Jean-Francois COLLIN"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ClinReport Vignette 1: Clinical Standards for Reporting Statistics}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Standards for reporting statistics

**ClinReport** enables to export tables an graphics of statistics according to the following standards:

>
*	Display the statistics by (treatment) groups in columns
*	Do not display horizontal or vertical lines in the body of the table 
*	Split vertically the results of several factor levels with empty rows
*	Add the number of subjects/observations in the column headers 
*	Each table is numbered (or can be numbered at least)
*	Each table have a title (or can be titled at least)
*	The number of digits are the same in all cells of the table
*	Police Headers are bolded
*	Use the *Times New Roman* police by default (can be changed if necessary)

Those are usually used for any scientific publications, including the reporting of epidemiological or clinical statistics. 

For quantitative statistics:

>
*	Report systematically the standard deviation between parenthesis after the mean: *mean(SD)*
*	Report the interval Q1 Q3 between brackets: *[Q1;Q3]*
*	Report the interval Min Max between brackets: *[Min;Max]*


For qualitative statistics:

>
*	Report the percentages and the number of observations *N(%)* or *%(N)*


For Least-Square Means statistics and P-values:

>
*	Report systematically the standard error between parenthesis after the estimate *estimate(SE)*
*	Report the 95% confidence interval between brackets: *[Lower Bound;Upper Bound]*
*	If P<0.001, display *P<0.001* instead of the value of P

#  Example with `ClinReport`

The purpose of the package **ClinReport** is to simplify the Statistical Reporting given the above standards.

They are the default options so few lines of code are necessary.

Example:

```{r, echo = TRUE, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(reshape2)
library(nlme)
library(emmeans)
library(car)
```  


```{r, include=TRUE}
library(ClinReport)
library(officer)
library(flextable)

data(datafake)

# Default quantitative stat desc

tab1=report.quanti(data=datafake,y="y_numeric",
		x1="GROUP",y.label="Quantitative response (units)",
		subjid="SUBJID",total=T)
		
# Default qualitative stat desc

tab2=report.quali(data=datafake,y="y_logistic",
		x1="GROUP",y.label="Qualitative response",
		subjid="SUBJID",total=T)

# Binding them into a single table

tab=regroup(tab1,tab2)

# In the R console, it looks like

tab

# Create formatted output for Microsoft Word or R markdown documents (like this one)

doc=report.doc(tab,title="Table of classic descriptive statistics (qualitative and quantitative parameter)",
		colspan.value="Treatment group", init.numbering =T )			

doc
```


By default, this table respect all the standards described above.

















