---
title: "ClinReport Vignette 3: Graphic Outputs"
author: "Jean-Francois COLLIN"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ClinReport Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Objective

In this vignette we will see the different graphics that you can produce with ClinReport.


## Get started

Start by loading all usual libraries.

```{r, echo = TRUE, message=FALSE, warning=FALSE}
library(ClinReport)
library(officer)
library(flextable)
library(dplyr)
library(reshape2)
library(nlme)
library(emmeans)
library(car)
```

Load your data.

```{r, include=TRUE}
# We will use fake data
data(data)
print(head(data))
```



### Quantitative graphics

First you need to produce a quantitative table using `report.quanti()` function
then you use the `plot()` function on the result: 


If there is no explicative variable, the corresponding graphic of the call to `report.quanti()`
is a barplot of the mean of the response value.

```{r}
# Only one numerical response

tab1=report.quanti(data=data,y="y_numeric")
plot(tab1,title="Mean (+/-SD) of y",add.sd=T,ylab="Mean Response value",xlab="")
```


If there is one explicative variable, the corresponding graphic will be a
barplot per treatment group.

You can personnalize the outputs using, the usual, `title` `xlab` `ylab` `ylim` etc.. options.

```{r}
#  one numerical response ; one explicative variable

tab2=report.quanti(data=data,y="y_numeric",x1="GROUP")
plot(tab2,title="Mean (+/-SD) of y per treatment group",add.sd=T,ylab="Mean of y",xlab="",
ylim=c(-1,8))
```

If there is also a second explicative variable. The corresponding plot will be a lineplot:

The means will be connected according to this second variable to capture the evolution
accross its different levels.


```{r}
#  one numerical response ; two explicative variable

tab3=report.quanti(data=data,y="y_numeric",x1="GROUP",x2="TIMEPOINT")
plot(tab3,title="Mean (+/-SD) of y per treatment group",add.sd=T,ylab="Mean of y",xlab="",
ylim=c(-1,8))
```




