---
title: "ClinReport Vignette 3: Modify the tables"
author: "Jean-Francois COLLIN"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ClinReport Vignette 3: Play With The Outputs}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Objective

In this vignette we will see how to modify your outputs.
Basically you can:

- Mix qualitative and quantitative descriptive statistics: `regroup()` function
- Choose the quantitative statistics you want to display: `report.quanti()` function
- Report row percentages instead of column percentages: `report.quali()` function
- Add a specific statistics to an existing table: `add.stat()` function
- Split an existing table in 2 parts: `split()` function
- Drop one or several levels of a variable in a table
- Transpose the statistics in columns

## Load the usual R packages

Start by loading all usual libraries.

```{r, echo = TRUE, message=FALSE, warning=FALSE}
library(ClinReport)
library(officer)
library(flextable)
library(emmeans)
```

Load your data.

```{r, include=TRUE}
# We will use fake data
data(datafake)
print(head(datafake))
```



## Mixed Quantitative and Qualitative statistics

You can mix qualitative and quantitative outputs. It's possible only if there is only 1 explicative variable, 
and it should be the same variable for both response:

```{r}
tab1=report.quanti(data=datafake,y="y_numeric",
		x1="GROUP",subjid="SUBJID",y.label="Y numeric")

tab2=report.quali(data=datafake,y="y_logistic",
		x1="GROUP",subjid="SUBJID",y.label="Y logistic")

tab3=regroup(tab1,tab2,rbind.label="The label of your choice")


report.doc(tab3,title="Mixed Qualitative and Quantitative output",
colspan.value="Treatment group")
```


## Report a specific quantitative statistic

You will have to specify the function corresponding to the statistics
and use the `func.stat` argument


```{r}
es=function(x) mean(x,na.rm=T)/sd(x,na.rm=T) 

tab=report.quanti(data=datafake,y="y_numeric",x1="GROUP",
total=TRUE,subjid="SUBJID",
func.stat=es,
func.stat.name="Effect size")

report.doc(tab,title="Example of a specific statistic reporting",
colspan.value="Treatment group")
```



## Add a specific statistics to an existing table


You can also add a specific (or several) statistics to an existing table.

Let's say you want the default statistics (mean, median, sd etc..)
plus some specific statistics like the mode or the coefficient of variation.

In this case, you can use the `add.stat()` function with the `pos` argument
to choose where you want to add this statistic:

```{r}
# The default statistics are given here:
 
tab1=report.quanti(data=datafake,y="y_numeric",x1="GROUP",total=TRUE,subjid="SUBJID")

 # Define the function corresponding to the coefficient of variation for example
 
cv=function(y) sd(y,na.rm=TRUE)/mean(y,na.rm=TRUE)
 
 # We use the add.stat function to add CV at the second row:
 
tab1.cv=add.stat(tab1,datafake,func.stat=cv,func.stat.name="Coef. Var",
 pos=2)

report.doc(tab1.cv,title="Example of adding a coefficient of variation")

 # Same with 2 explicative variables
 
tab=report.quanti(data=datafake,y="y_numeric",x1="GROUP",
 x2="TIMEPOINT",total=TRUE,subjid="SUBJID",
		at.row="TIMEPOINT")
 
 tab=add.stat(tab,datafake,func.stat=cv,func.stat.name="Coef. Var",
 pos=2)

 
 # And on position 5, we can add for example the mode
 
 mode=function(x)
 {
   x=na.omit(x)
   ux <- unique(x)
   ux[which.max(tabulate(match(x, ux)))]
 }
 
 
 tab=add.stat(tab,datafake,func.stat=mode,func.stat.name="Mode",pos=5)
 
 report.doc(tab,title="Example of adding 2 more statistics in an existing table",
 colspan.value="Treatment Group")

```



## Row or column percentages

If you want to display the row percentages instead of column percentages in
`report.quali()` function, you just have to set the argument `percent.col` to `FALSE`: 


```{r}
tab=report.quali(data=datafake,y="y_logistic",x1="GROUP",
total=TRUE,subjid="SUBJID",percent.col=FALSE)

report.doc(tab,title="Example of row percentage reporting",
colspan.value="Treatment group")
```



## Drop levels of a factor in the tables

If you want to drop some levels in the table, you can use
'drop.x1' drop.x2' or 'drop.y' if 'y' is a qualitative variable.

For example. If we just want the statistics of group A:

```{r}
tab=report.quali(data=datafake,y="y_logistic",x1="GROUP",
subjid="SUBJID",drop.x1=c("B","C"))

report.doc(tab,title="Example of row percentage reporting",
colspan.value="Treatment group")
```

## Drop  missing values

Sometimes it can be useful to remove the missing values so that percentages are
computed only on non missing observations.
For that, just use the 'remove.missing' argument in 'report.quali':

```{r}
tab=report.quali(data=datafake,y="y_logistic",x1="GROUP",
remove.missing=TRUE)

report.doc(tab,title="Example of droping missing values",
colspan.value="Treatment group")
```



## Transpose LS-Means


```{r}
mod=lm(y_numeric~GROUP,data=datafake)
pairs=pairs(emmeans(mod,~GROUP))

tab=report.lsmeans(pairs,transpose=TRUE)

report.doc(tab,title="Example of transposing LS-Means in column",
colspan.value="Treatment group")
```




