---
title: "ClinReport Vignette 2: Get Started"
author: "Jean-Francois COLLIN"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ClinReport Vignette 2: Get Started}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Get started

Start by loading all usual libraries.

```{r, echo = TRUE, message=FALSE, warning=FALSE}
library(ClinReport)
library(officer)
library(flextable)
library(dplyr)
library(reshape2)
library(nlme)
library(emmeans)
library(car)
```

Load your data.

```{r, include=TRUE}
# We will use fake data
data(data)
print(head(data))
```

Create a statistical output for a quantitative response and two explicative variables.
For example a treatment group and a time variable corresponding to the visits of a clinical trial.

For that we use the `report.quanti()` function:

```{r, include=TRUE}
tab1=report.quanti(data=data,y="y_numeric",
		x1="GROUP",x2="TIMEPOINT",at.row="TIMEPOINT",
		subjid="SUBJID")

tab1
```  


The `at.row` argument is used to space the results between each visit and the `subjid` argument is used
to add in the columns header the total number of subjects randomized by treatment group.


Generally we want also the corresponding graphics. So you can use the specific plot function
to print the corresponding graphic of your table:


```{r, include=TRUE}
g1=plot(tab1,title="The title that you want to display")
print(g1)
```  

You can modify the plot by using the following arguments of the `plot.desc()` function:

```{r, include=TRUE}
args(ClinReport:::plot.desc)
``` 


Then we can use the `report.doc()` function which use the **flextable** package to format
the output into a `flextable` object, ready to export to `Microsoft Word` with the **officer** package.

The table will look like this (we can have a preview in HTML, just to check):

```{r, include=TRUE}
report.doc(tab1,title="Quantitative statistics (2 explicative variables)",
		colspan.value="Treatment group", init.numbering =T )			
```

All output numbers will be increased automatically after each call of the function `report.doc()`.

You can restart the numbering of the outputs by using `init.numbering=T` 
argument in `report.doc()` function.

Finally, we add those results to a `rdocx` object:

```{r}
doc=read_docx()
doc=report.doc(tab1,title="Quantitative statistics (2 explicative variables)",
		colspan.value="Treatment group",doc=doc,init.numbering=T)
doc=body_add_gg(doc, value = g1, style = "centered" )
```

Write the doc to a docx file:

```{r results='hide'}
file=paste(tempfile(),".docx",sep="")
print(doc, target =file)

#Open it
#shell.exec(file)
```


## The different outputs

### Qualitative tables


An example of qualitative statistics with one explicative variable

```{r}
tab=report.quali(data=data,y="y_logistic",
		x1="VAR",total=T,subjid="SUBJID")
		
report.doc(tab,title="Qualitative table with two variables",
colspan.value="A variable")	

 ```

An example of qualitative statistics with two explicative variables

```{r}
tab=report.quali(data=data,y="y_logistic",
		x1="GROUP",x2="TIMEPOINT",at.row="TIMEPOINT",
		total=T,subjid="SUBJID")
		
report.doc(tab,title="Qualitative table with two variables",
colspan.value="Treatment group")	

 ```

### Quantitative tables



An example of quantitative statistics with one explicative variable

```{r}
tab=report.quanti(data=data,y="y_numeric",
		x1="VAR",total=T,subjid="SUBJID")
		
report.doc(tab,title="Quantitative table with one explicative variable",
colspan.value="A variable")	

 ```

An example of quantitative statistics with two explicative variables

```{r}
tab=report.quanti(data=data,y="y_numeric",
		x1="GROUP",x2="TIMEPOINT",at.row="TIMEPOINT",
		total=T,subjid="SUBJID")
		
report.doc(tab,title="Quantitative table with two explicative variables",
colspan.value="Treatment group")	
 ```



### Mixed Quantitative and Qualitative tables

You can mix qualitative and quantitative outputs.

But it's only possible for 1 explicative variable, 
and it should be the same variable for both response:

```{r}
tab1=report.quanti(data=data,y="y_numeric",
		x1="GROUP",subjid="SUBJID",y.label="Y numeric")

tab2=report.quali(data=data,y="y_logistic",
		x1="GROUP",subjid="SUBJID",y.label="Y logistic")

tab3=regroup(tab1,tab2,rbind.label="The label of your choice")


report.doc(tab3,title="Mixed Qualitative and Quantitative outputs",
colspan.value="Treatment group")
```

### Anova model reporting

For the anova table reporting, it's basically a call
to the function `xtable_to_flextable()`. The function
`report.doc()` just handle the numbering of the output
and the header with the title.

```{r}
# Removing baseline data for the model
data.mod=droplevels(data[data$TIMEPOINT!="D0",])

mod=lme(y_numeric~baseline+GROUP+TIMEPOINT+GROUP*TIMEPOINT,
random=~1|SUBJID,data=data.mod,na.action=na.omit)
 
anov3=Anova(mod,3)

report.doc(anov3,title="Mixed Qualitative and Quantitative output")
```


### LS-Means model reporting

LS-means reporting are based on the package **emmeans**.
The function `report.lsmeans()` enables to format the output:

```{r}
lsm=emmeans(mod,~GROUP|TIMEPOINT)

tab=report.lsmeans(lsm,at.row="TIMEPOINT")

report.doc(tab,title="LS-Means example",
colspan.value="Treatment Group")
```


### Pairs and Contrasts of LS-MEans

It's the same usage


```{r}
contr=contrast(lsm, "trt.vs.ctrl", ref = "A")

# There is just only one explicative variable

tab.contr=report.lsmeans(lsm=contr,at="TIMEPOINT")
		
		
report.doc(tab.contr,title="LS-Means contrast example",
colspan.value="Contrasts")		
```













